\label{related_literature}



\drghosh{\textbf{Section organization.} The 'Context of Civil Conflict' paragraph is institutional background, not literature. Split into TWO sections: Section 2 'Background: The Nepal Civil War' (institutional context, timeline, geography of insurgency, key events 1996/2001/2006, end of war + Comprehensive Peace Accord) and Section 3 'Related Literature'. Add a conflict timeline figure and a casualties-over-time figure.}



\drghosh{\textbf{Suggested literature subsection structure.} 3.1 Conflict and economic outcomes (Voors et al. 2012; Blattman \& Miguel 2010 survey; Bellows \& Miguel 2009). 3.2 Conflict and migration (Bohra-Mishra \& Massey 2011; Engel \& Ibanez 2007; Adhikari 2013; Calderon \& Ibanez 2009). 3.3 Childhood exposure to violence and long-run outcomes (Akresh et al. on Rwanda/Burundi; Bundervoet et al. 2009; Akbulut-Yuksel 2014; Leon 2012). 3.4 International migration from Nepal (Seddon et al. 2002; Lokshin \& Glinskaya 2009; Sharma \& Gurung; Maharjan et al.). Close the section with a clear statement of how you contribute to each.}



\drghosh{\textbf{Citations needed.} Good substantively. But the claim that political/economic exclusion drove the conflict is a secondary literature claim — cite specific sources (Hutt 2004; Murshed \& Gates 2005; Do \& Iyer 2010 on geography of Nepal conflict). The Do \& Iyer paper is very close to your identification strategy and MUST be cited.}




\drghosh{\textbf{Replace with concrete papers.} You raise interesting questions (direct vs. indirect effects; internal vs. external) but you don't review any actual papers that have addressed them. Replace this paragraph with concrete citations and findings, then state which side your paper is on (internal AND external, long-run, childhood exposure).}

Various literature have discussed on the direct and indirect effect of violence on migration. Indirect effect relate to economic dislocation or economic turmoil causing people to migrate from their usual place of residence while the direct effect imply the threat of staying back rather than economic costs, push the households to move away. How does the violence impact migration- internal and external, differently is another issue.