

\drghosh{\textbf{Channels: most important section.} Empty — and this is the most important section for your contribution. Your headline finding (negative coefficients) is the OPPOSITE of the 'flight from conflict' story. You need a credible explanation. Candidate channels: (i) Liquidity / poverty trap — international migration to Gulf is expensive (\textasciitilde{}\$1,000–2,000 in recruitment fees); conflict reduces parental wealth  to  kids can't afford migration. TEST: interact treatment with parental wealth proxies (asset index from NLFS). (ii) Education channel — conflict disrupted schooling  to  lower returns to migration. TEST: mediation analysis with years of education; restrict sample to those who completed secondary. (iii) Network channel — conflict disrupts village migration networks. TEST: heterogeneity by pre-conflict village migration rates (if available in NLSS waves). (iv) Risk preferences — Voors et al. (2012) show conflict EXPOSURE INCREASES risk tolerance. If anything, this would predict MORE migration, not less. The contradiction is interesting — discuss. (v) Household composition — orphans, sibling structure. NLFS may have household roster info. (vi) Direct displacement — kids who fled internally during conflict may have used up their 'migration budget' early. TEST: condition on internal-migration history. Lay these out, test what you can, be honest about what you can't identify.}

\label{mechanism}
% \subsection{Occupation Channel}
% \input{Channel/Occupation Channel}

% \newpage
% \subsection{Education Channel}
% \input{Channel/Education Channel}